---
title: "Coursera Week 4 - oneVsAll"
output:
  html_document:
    toc: true
    depth: 2    
---
[ML Home](../index.html)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE}
library(tidyverse)
```

# lrCostFunction

## Test Case

***

# oneVsAll


## Test Case

***

# predictOneVsAll(all_theta, X)

## Test Case
```
clear;clc;
all_theta = [1 -6 3; -2 4 -3]
X = [1 7; 4 5; 7 8; 1 4]
predictOneVsAll(all_theta, X)

%output:
% ans =
%    1
%    2
%    2
%    1
```

- Each row of all_theta is the theta coefficients learned for the i-th class
- So all_theta is a k by n matrix, where k is the number of classes and n is the number of features. 

- 2x3
- all_theta is (num_labels x n), 2x3, kxn, 2 classes, 3 features
- num_labels = 2
- X is mxn - 4x2 - 4 training rows, 
- n = 2 - number of features
- m = 4 - number of training examples
- result of (m x num_labels)
- result = 4 x 2 = X * 
- max(result) % Returns column index with largest value

## Octave Session Initialize Variables

### all_theta

2x3

```
>> all_theta = [1 -6 3; -2 4 -3]
all_theta =

   1  -6   3
  -2   4  -3

% 4x2
```

### X
m x n
```
>> X = [1 7; 4 5; 7 8; 1 4]
X =

   1   7
   4   5
   7   8
   1   4
```
### Add 1's row vector to column 1 of X

### Multiplication Result



## Octave Session

4x2 * 2*3 = 4x3
```
X * all_theta
ans =

  -13   22  -18
   -6   -4   -3
   -9  -10   -3
   -7   10   -9
```

Get help on max function
```
help max
```

# R Solution

```{r}
all_thetas <- matrix(c(1, -6, 3, -2, 4, -3), nrow = 2, ncol = 3, byrow = TRUE)
all_thetas
```
```{r}
X <- matrix(c(1, 7, 4, 5, 7, 8, 1, 4), nrow = 4, ncol = 2, byrow = TRUE)
X   
```

```{r}
y = X %*% all_thetas
y
```

```{r}
# z = as_tibble(y)

#rowMax(y, value = FALSE)
library(matrixStats)

rowMaxs(y, value = FALSE)

```

# References

- [Programming Tutorials](https://www.coursera.org/learn/machine-learning/discussions/weeks/4/threads/Hfo82qxTEeWjcBKYJq1ZMQ)
- [Test Case](https://www.coursera.org/learn/machine-learning/discussions/all/threads/5g8LaZTCEeW0dw6k4EUmPw)
- [max discussion](https://www.coursera.org/learn/machine-learning/discussions/all/threads/ERsT4cRKEeaYcRJ-aKpq1A)
